---
title: "Aaron Coyner's CV"
author: Ted Laderas
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1RAbfDiqCQKw3cmEaFZlj2AkBZRG5YjRMHl9-U2ZZZoI/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _aaroncoyner.github.io/cv_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/aaroncoyner/cv/raw/master/cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.



Main
================================================================================

Aaron Coyner, PhD(c) {#title}
--------------------------------------------------------------------------------

**PhD Candidate**, Division of Bioinformatics and Computational Biomedicine, Department of Medical Informatics and Clinical Epidemiology

**Researcher**, Casey Eye Institute

Oregon Health & Science University

My research is centered around the detection and prediction of retinopathy of prematurity using a deep learning approach.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Patents {data-icon=file-text}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('patent')
```


Peer-Reviewed Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```


Conference Presentations {data-icon=users}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('conference')
```


Code Repositories {data-icon=github}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('repo')
```


Teaching and Work Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('positions')
```


Relevant Coursework {data-icon=book-open}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("course")
```


Volunteer Experience {data-icon=bookmark}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section("volunteer")
```




```{r}
CV %<>% print_links()
```